Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-07-28 literature/paper_draft.qmd
expand on tourism section, included modelling and cross validation

We measure the tourism demand using “visitor nights,” the total number of nights spent by Australians away from home. The data is collected via the National Visitor Survey, managed by Tourism Research Australia, using computer assisted telephone interviews from nearly 120,000 Australian residents aged 15 years and over [@tourismau-jk]. The data are monthly time series spanning from January 1998 to December 2019, resulting in 264 observations per series, producing a canonical "$n \ll p$" setting for which high-dimensional covariance estimators were designed. This is particularly well-suited to evaluate forecast reconciliation methods, because the extreme dimensionality over sample size mirrors many comptemporary business problems, for instance, Starbucks drink sales.

@@

>>>>

<!-- Table to illustrate the hierarchy -->

We measure the tourism demand using “visitor nights,” the total number of nights spent by Australians away from home. The data is collected via the National Visitor Survey, managed by Tourism Research Australia, using computer assisted telephone interviews from nearly 120,000 Australian residents aged 15 years and over [@tourismau-jk].

The data are monthly time series spanning from January 1998 to December 2019, resulting in 264 observations per series, producing a canonical "$n \ll p$" setting for which high-dimensional covariance estimators were designed. This is particularly well-suited to evaluate forecast reconciliation methods, because the extreme dimensionality over sample size mirrors many contemporary business problems, for instance, Starbucks drink sales. Tourism demand is also economically important and notoriously volatile; the heterogeneous regional and purpose‑specific patterns create a realistic stress‑test for reconciliation algorithms. Using this panel therefore provides both a compelling policy context and a stringent statistical laboratory for comparing between reconciliation methods, especially those that rely on regularised covariance estimation or exploit cross‑sectional information to stabilise forecasts when historical data are scant.

@@

We evaluate the performance of reconcilation methods using a rolling window cross validation process. We set the training window to be 96 observations, which serves as a training set to obtain the best-fitted ARIMA models for each of 560 series by minimising AICc, in which we use the automatic algorithm from Fabletools R package [@fabletools-fa]. The 1- to 12-step-ahead base forecasts are then generated by these ARIMA models. These base forecasts are combined or reconciled using alternative strategies to obtain reconciled forecasts. We repeat the procedure by rolling the training window by one observation at a time, until December 2018. This results in a total of 156 windows, with corresponding 156 sets of 1- to 12-step-ahead forecasts for each of 560 series.

Regarding reconciliation strategies, we consider OLS, mint_shr (MinT with Shrinkage estimator), and mint_n (MinT with NOVELIST estimator). Note that the number of series is larger than the number of observations (560 compared to 96), hence the sample covariance matrix is not positive definite and will not be used.
